---
title: "Credit Elasticities in Less-Developed Economies"
description: "Implications for Microfinance"
author:
  name: "Finn Deike"
  url: https://github.com/finndeike/thesis_code_rep
  affiliation: University of Ulm
output: 
  html_document:
    keep_md: yes
    toc: yes

---

```{r setup, include=FALSE, echo=FALSE}
# Load Libaries
library(haven)
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
library(stargazer)
library(qwraps2)
library(AER)
library(VGAM)
library(censReg)
library(statar)
library(regtools)
library(gridExtra)
library(RTutor)
options(qwraps2_markup = "markdown")

# options for rendering data frames
RTutor::set.knit.print.opts(html.data.frame=FALSE, table.max.rows=25, round.digits=8, signif.digits=8)

# knitting even if there is an error
knitr::opts_chunk$set(error = TRUE)

```

**An Interactive Anaylsis in R**


Welcome to my interactive RTutor Problemset, containing the main results from the paper **Credit Elasticities in Less-Developed Economies: Implications for Microfinance** by Dean S. Karlan (Department of Economics, Yale University) and Jonathan Zinma (Department of Economics, Dartmouth College) published by the American Economic Review in 2008.


# Exercise Content

1. Introduction 

2. Data Overview

3. Theoretical Model

4. Regression Analysis

5. Estimation

6. Conclusion

7. Appendix

8. References



## Introduction


## Data Overview

wdghwugfeuifgef
efhehf
fhefhew

***
### Info: How do we read a Stata File in R?

**read_dta** reads a file in Stata version 5-12 binary format into a data frame in R. This funtion only supports Stata formats after 12, but since we have a 5-12 format it can be used.

```{r "1", eval=FALSE}
library(haven)
stata_data <- read_dta("~/Documents/GitHub/thesis_code_rep/kz_demandelasts_aer08.dta")
```

***










